Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-10 paper/sec-results.tex
work on paper

\section{Background decomposition}

Up to now we have considered the effects of all backgrounds added
together, except in Table~\ref{table:cutflow4B} and the corresponding
discussion where we have studies how our
results are modified if only the QCD $4b$ background is included.
%
In this section we study the decomposition of the background in each
of its individual components, for the three different categories
of events used in this work.

>>>>

\subsection{Background decomposition}

Up to now we have considered the effects of all backgrounds added
together, except in Table~\ref{table:cutflow4B} and the corresponding
discussion where we have studies how our
results are modified if only the QCD $4b$ background is included.
%
In this section we study the decomposition of the background in each
of its individual components, for the three different categories
of events used in this work.
%

In Table~\ref{table:cutflowBack}   we show the results for the cross-sections for the different
backgrounds that we consider at the end of the cut-based analysis, for each
of the three categories.
%
All the backgrounds have been normalized to known higher-order results,
as summarized in Table~\ref{tab:samples}.
%
As we can see from this comparison, as opposed that what naively one would expect,
the QCD $2b2j$ background turns out not to be negligible as compared to the $4b$
multijets in any of the categories.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{c|c|c|c}
    \hline
    Background  &    \multicolumn{3}{c}{$\sigma$ (fb)}   \\
    \hline
  &    Resolved  &  Intermediate  &   Boosted \\
    \hline
    \hline
  QCD $4b$   &   $9.9\,10^{2}$       &  $59$       &   $7.1$        \\
  QCD $2b2j$ &   $2.4\,10^{3}$       &  $6.4\,10^{2}$       &   $3.5$        \\
  QCD $4j$ &     $1.7\,10^{2}$       &   $22$      &    $2.1$        \\
  $t\bar{t}$ &   $3.6$       &  $2.2$       &   $4.5\,10^{-2}$        \\
  \hline
  \hline
Total     &    $3.6\,10^{3}$      &   $7.2\,10^{2}$      &     $13$      \\
\hline
\end{tabular}
    \caption{\small The cross-sections for each of the individual background
      components (and their total sum) at the end of the cut-based
      analysis, for each of three categories.
    \label{table:cutflowBack}
    }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the boosted case, the sum of the $2b2j$ and $4j$ components is almost as large as the
irreducible $4b$ background, thus increasing the total background rates by a factor 2 as compared
to the case where only $4b$ is accounted for.
%
This effect is more dramatic in the intermediate and resolved categories: in the former,
$2b2j$ completely dominates the background (thus the increase in $S/sqrt{B}$ noted in
Table~\ref{table:cutflow4B}  when only the $4b$ component is kept), and in the latter
it is comparable to $4b$.
%
Therefore, we conclude that an accurate estimate of the fake $b$-tag contribution is
an essential component of this analyses, and that complete QCD multijet samples
should be included.

  {\bf add plots BKG}

  One might ask why the $2b2j$ process
  is not subdominant as compared to $4b$: while its generator-level cross-section is
  much larger, $\sigma_{2b2j} \simeq 240\sigma_{4b}$, one expects a suppression
  of the order of $f_l^2 =10^{-4}$ since only with two light jets mistagged as $b$-jets the event
  would be identified as a Higgs candidate.
  %
  We have checked that this expectation is true only at parton level: once parton shower effects
  are accounted for, both the radiation of $b\bar{b}$ pairs from the shower and combinatorics increase
  the number of $b$ quarks in the final state, enhancing substantially the $2b2j$ rates as compared
  to the naive parton level expectation.
  %
  To verify this, we plot the number of $b$-quarks.....
